---
title: "Fantasy Football Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ESPN Website Equivalent Functionality}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
if (!interactive()) {
  options(width = 90)
}
```

```{r setup}
library(fflr)
packageVersion("fflr")
ffl_id(leagueId = "42654852")
```

This vignette will demonstrate the fflr functions used to reach equivalency
with the ESPN fantasy football website. The website has eight section headers
with various subsections:

1. My Team
    * Overview
    * Stats (TBD)
    * Schedule (TBD)
    * News
    * Projections (TBD)
    * Ranks (TBD)
2. League
    * League Home
    * Settings
    * Members
    * Rosters
    * Schedule
    * Message Board
    * Transaction Counter
    * History
    * Draft Recap
    * Email League
    * Recent Activity
3. Players
    * Add Players
    * Watch List
    * Scoring Leaders
    * Live Draft Trends
    * Points Against
    * Added / Dropped
    * Player News
    * Projections
    * Budget Summary
    * Offers Report
    * Stat Corrections
4. FantasyCast
5. Scoreboard
6. Standings
7. Opposing Teams
8. LM Tools
    * League Membership Tools
    * Draft Tools
    * League and Scoring Settings Tools
    * Roster Tools
    * Schedule and Standings Tools
    * Miscellaneous Tools

## My Team

The _My Team_ page presents an overview of, well, your fantasy team. From this
page, a team manager can set their lineup and see statistics and news on the
players on their roster.

There are six subsections on the _My Team_ page.

### Overview

The `team_roster()` function returns _all_ rosters in a league. The output of
this function is organized to replicate the layout of the table found on the
website. Players are listed in order of their "slot" with name and team 
information followed by projected and actual scores and ownership statistics.

```{r team-roster}
my_team <- team_roster(scoringPeriodId = 1)[[1]] # select first roster
my_team[, -(1:3)]
```

### News

The `player_outlook()` and `player_news()` functions return news on your roster.
The first returns _all_ outlooks by player and week and cannot be refined beyond
setting a `limit` of players to return (in order of rank).

```{r player-outlook}
player_outlook(limit = 1)
```

The second fiction takes a single `playerId` value and returns all the recent
news on that player, including premium stories in HTML format.

```{r player-news}
player_news(playerId = "3139477", parseHTML = FALSE)
```

## League

ESPN fantasy leagues have their own unique settings and structure. This package
has been tested for a very narrow subset of those possible settings.

```{r league-info}
league_info(leagueId = "42654852")
league_name()
league_size()
str(league_status())
```

### Settings

#### Draft

```{r draft-settings}
draft_settings()
```

#### Rosters

```{r roster-settings}
roster_settings()
```

#### Scoring

```{r score-settings}
scoring_settings()
```

#### Transactions and Keepers

```{r waiver-settings}
acquisition_settings()
```

#### Schedule

```{r schedule-settings}
schedule_settings()
```

### Members

```{r league-members}
league_members()
```

### Rosters

```{r team-roster-all}
team_roster(scoringPeriodId = 1)
```

### Schedule

```{r tidy-matchups}
tidy_matchups(scoringPeriodId = 1)
```

### Message Board

```{r league-messages}
league_messages(scoringPeriodId = 1)
```

### Transaction Counter

```{r transaction-counter}
transaction_counter()
```

### Draft Recap

```{r draft-recap}
draft_recap()
```

### Recent Activity

```{r roster-moves}
recent_activity(scoringPeriodId = 1)
```

## Players

```{r all-players}
all_players(limit = 10)
```

## Scoreboard

```{r live-scoring}
live_scoring()
```

## Standings

```{r league-standings}
league_standings()
```
