---
title: "fantasy-football"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fantasy-football}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
if (!interactive()) {
  options(width = 99)
}
```

```{r setup}
library(fflr)
packageVersion("fflr")
```

The fflr package helps easily access data from the ESPN fantasy football v3 API.
Both current and historical data can be 

## Games

Some functions work independently of your specific league. As of now, this
package only works with data from fantasy football leagues, but other fantasy
sports exist.

```{r espn_games}
espn_games()
```

This package is designed to retrieve both current and historical data from the
ESPN API. There are 17 years of seasons listed in the API!

```{r ffl_seasons}
ffl_seasons()
```

The current season and scoring period are pieces of data that can be easily
accessed and referenced for data manipulation.

```{r ffl_info}
str(ffl_info())
```

```{r ffl_now}
ffl_year()
ffl_week()
```

To easily refer to past or future years and weeks, simply add an offset integer.

```{r ffl_past}
ffl_year(offset = -2)
ffl_week(offset =  1)
```

## Leagues

To access data on your league you will need to first use the league manager
tools to make your league viewable to the public. This [ESPN help page][1]
explains how this can be done; the option is found in the basic settings section
of the fantasy football website.

[1]: https://support.espn.com/hc/en-us/articles/360000064451-Making-a-Private-League-Viewable-to-the-Public

Once your league is set to public, you'll need to find the unique numeric league
ID found in the URL of any page. This league ID (LID) is needed to access league
specific information like rosters, scores, and transactions.

<pre>
https://fantasy.espn.com/football/league?leagueId=<b>252353</b>
</pre>

For convenience, the `lid` argument to most functions defaults to looking for
an "lid" global option. Use `options()` to set your league ID and put the line
in your `~/.Rprofile` file to set at start up.

```{r options}
options(lid = 252353)
```

With our league ID option set, we can now easily retrieve league information.

```{r league_info}
str(league_info())
```

As we can see, my league this season has 8 teams and runs for 16 weeks.

Before we look into fantasy scores and player data, we'll look a little more
into how our league is set up.

We can identify the league members and the fantasy teams they own. Fantasy teams
can have multiple owners, so team owners are identified by a nested list of
unique member hashes.

```{r league_members}
league_members()
```

League teams are occasionally only identified by their team number instead of
their nickname or abbreviation. The data frame returned by `league_teams()` can
be used to convert these team numbers.

```{r league_teams}
(teams = league_teams())
```

The `team_abbrev()` function makes this conversion simple.

```{r team_abbrev}
team_abbrev(id = 6, teams)
```

One caveat about the design of this package: most of the functions were designed
and tested using the settings from the author's own fantasy league. Functions
relying on certain scoring or roster settings are particularly vulnerable for
the time being. These settings can be referenced with the `*_settings()`
functions and may be integrated in the future.

```{r roster_settings}
roster_settings()
score_settings()
```

## Players

There are over a thousand players in the NFL eligible for fantasy football. The
full list of current players can be retrieved at any time.

```{r all_players}
all_players()
```

Each player is identified by their unique ID. Sometimes, only those player IDs
are given. Team positions like defenses have negative IDs, but information on
individual players can be retrieved from the generic ESPN (non-fantasy) API.

```{r player_info}
player_info(id = 3054850, row = TRUE)
```

For your convenience, a table of active players is saved as a data frame.

```{r nfl_players}
nfl_players
```

News on an individual player can also be helpful.

```{r player_news}
player_news(id = 15847)
```

ESPN analysts publish weekly and preseason outlooks on most players.

```{r player_outlook, results='asis'}
outlooks <- player_outlook()
nrow(outlooks)
cat(paste(">", outlooks$outlook[1]))
```

## Rosters

For the team rosters in your league, a list of data frames can be returned.

```{r team_roster}
rosters <- team_roster()
```

The elements of this list are named for their team abbreviation.

```{r my_roster}
rosters$KIER
```

We can easily identify the current starting roster, dropping bench players and
those on injury reserve.

```{r start_roster}
start_roster(rosters$KIER)
```

We can also easily filter for the starting roster that has the highest projected
or past score. The score total for that roster can also be easily summed.

```{r best_roster}
(best <- best_roster(rosters$KIER))
roster_score(best)
```

Players on a roster can also be compared against their professional schedule.

The 2020 NFL schedule is saved as the `nfl_schedule` table. This table might
be out of date due to rescheduled games. The current schedule can be returned
by `pro_schedule()`. The table also indicates if the games have started yet.

```{r pro_schedule}
(sched <- ffl_merge(
  x = rosters$KIER[, 1:9], 
  y = pro_schedule()
))
```

The opponent teams for each player are ranked by the average points scored
against them by each position. The lower the rank, the more points that position
scores against the opponent team.

```{r opponent_ranks}
ffl_merge(
  x = sched[, 6:10], 
  y = opponent_ranks(), 
  by = c("pos", "opp" = "pro")
)
```

## Transactions

If you're interested in how the players on a roster were acquired you look at
either the acquisition history, draft picks, or league roster moves.

Every roster identifies players by acquisition method.

```{r player_acquire}
player_acquire()[[5]]
```

Roster moves are any waiver add, lineup change, or trade. Roster moves only
identify players by their ID, so we will merge with the players table. The
`ffl_merge()` function uses `merge()` to return a tibble of combined columns
and rows in their same order.

```{r roster_moves}
ffl_merge(
  x = roster_moves()[, 7:14], 
  y = nfl_players[, 1:3]
)
```

We can also get the entire history of the draft, either snake or auction.

```{r draft_picks}
ffl_merge(
  x = draft_picks(), 
  y = nfl_players[, 1:3]
)
```

A summary of transactions and moves is also available.

```{r moves_summary}
moves_summary()
```

## Scores

Past team scores are found in the tidy tibble by matchup period.

```{r match_scores}
match_scores()
```

These scores are only for matches played. We can also determine future matches.

```{r match_schedule}
match_schedule()
```

If a matchup period is currently ongoing, the live score and projection can
also be found.

```{r live_scoring}
live_scoring()
```

It's worth noting that matchups and weeks are different units of time. For this
league, for example, regular season matchups last one week and playoff matches
last two.

```{r schedule_settings}
schedule_settings()
```

If you want to return scores by _week_, use a different function. These
functions also return "power wins" which are the total number of wins a team
would get if they played every other team in the league; the lowest score gets
zero power wins and the highest gets one less than the number of teams.

```{r week_scores}
week_scores()
```

A summary of scores and wins is also available.

```{r score_summary}
score_summary()
```

## Historical

Most functions have an `old` argument that can be used to specify access to the
historical endpoint of the API. If the recent data is usually returned as a 
dataframe, like rosters, then a _list_ of dataframes is returned instead; if the
recent data is a list, then a single dataframe is returned instead.

```{r past_scores}
past <- week_scores(old = TRUE)
names(past) <- 2015:2019
str(past, max.level = 1)
```

```{r past_info}
str(league_info())
league_info(old = TRUE)
```
